---
title: "HW2"
author: "claire"
date: "2018年9月21日"
output: html_document
---
## 2.8
##### a.2391 people
##### b.People aged 65 or older
##### c."People who attended a religious service once a week and prayed or studied the Bible once a day"&"less likely to have high blood pressure"
##### d.Sample data.Since they only observed a certain group of people rather than everyone who matches the standards.

## 2.20
##### the explanatory variable is "Whether a person smoking or not",and it is a categorical variable; the response variable is "Likely to develop Alzheimer's disease and other forms of dementia", and it is categorical qantitative.

## 2.30
### a.
```{r}
(1700/2470)*100
```

##### About 69%

###b.
```{r}
1056/1700*100
```

##### About 62%

###c.
```{r}
300/657*100
```

##### About 46%

###d.
```{r}
41/113*100
```

##### About 36%

## 2.32
###a.
```{r}
library(ggplot2)
age<-c("<20","20~24","25~29","30~34","35 and over")
per<-c(20.9,30.6,24.7,15.7,8.1)
firkid<-data.frame(age,per)
firkid
```
```{r}
ggplot(firkid,aes(x=age,y=per))+geom_col()
```
```{r}
barplot(per, col=rainbow(5),legend = rownames(age),xlab="Age")
```

### b.
```{r}
lbls<-age
pie(per, labels = age,  main="ReligImp") 
```
### c.
##### I think the pie chart is more informative because the data frame has a column of peercentage data, which is better to be shown by the pie chart.

##2.46
###a.
```{r}
num<-c(220,20,50,450,300,30,20,50,200,35,25,50,250,100,0,100,20,13,200,2,125,150,90,60)
CD<-data.frame(num)
summary(CD)
```
```{r}
stem(CD$num,scale = 1)
```

###b.
```{r}
hist(CD$num, breaks=20, col="light green",main="CD",xlab = "amount of CD")
```

```{r}
ggplot(CD,aes(x=num))+geom_histogram()
```

### c. 
##### Skew-right

## 2.52
### a.
```{r}
ceodata08 <- c(42,47,48,49,49,50,50,50,50,51,51,51,52,54,54,55,55,55,55,56,57,57,57,57,57,58,58,59,59,60,60,60,61,61,62,62,62,62,62,63,63,64,64,64,64,67,67,69,74,78)
ceo<-data.frame(ceodata08)
hist(ceodata08, breaks=10, col="light blue", main="Salary Distribution", xlab="$")
```

###b.
```{r}
stem(ceodata08,scale = 1)
```

###c.
```{r}
dotchart(ceodata08, cex=1, lcolor = NULL)
```

###d.
##### Skew-right

###e.
##### Yes, it's 78
```{r}
ggplot(ceo,aes(x=1,y=ceodata08))+geom_boxplot()
```

###f.
##### I think outkiers would be more likely to occur in the salaries of heads of heads of companies since they tended to be strong enough yo give high salaries.
##### On the other hand, the ages of companies have weaker relationship between the outlier of salaries distribution.

## 2.66
```{r}
blood<-c(110,123,132,150,127,118,102,122)
summary(blood)
```
###a.
##### 122.5

###b.
##### lower quartile:116
##### upper quartile:128.2

###c.
```{r}
128.2-116
```
##### interquartile range:12.2

### d.
```{r}
min<-quantile(blood,na.rm = TRUE)[2]-1.5*IQR(blood, na.rm = T)
min
max<-quantile(blood,na.rm = TRUE)[4]+1.5*IQR(blood, na.rm = T)
max
```

##### there is a outlier in this data since 150>146.625, so 150 is a outlier.

### d.
```{r}
bloodd<-data.frame(blood)
ggplot(bloodd,aes(x=1,y=blood))+geom_boxplot()
```

##2.76
#####a.
```{r}
g1<-c(2,30,35,70,100,120,135,150,190,200)
summary(g1)
```
#####b.
```{r}
g2<-c(8,12,16,29,35,40,45,46,95)
summary(g2)
```

###c.
```{r}
r1<-200-2
r1
r2<-95-8
r2
```
##### the range of Group1 is 198
##### the range of Group2 is 87

###d.
```{r}
g3<-c(2,30,35,70,100,120,135,150,190,200,8,12,16,29,35,40,45,46,95,NA)
g4<-c("g1","g1","g1","g1","g1","g1","g1","g1","g1","g1","g2","g2","g2","g2","g2","g2","g2","g2","g2","g2")
group<-data.frame(g3,g4)
ggplot(group,aes(x=1,y=g3))+geom_boxplot()+facet_grid(~g4)
```
##2.96
##### I would be more satisfied if the standard deviation was 5.
##### if the standard deviation was 5, the z-Score is (80-70)/5=2, which meant that my score was higher than most of my classmates.
##### if the standard deviation was 15, the z-Score is (80-70)/15=0.67, which meant that my score was higher than many people yet not the most of people.

##2.104
### To do 1
```{r}
smaller_head_circu<-56-2-2
smaller_head_circu
```
### To do 2
```{r}
larger_head_circu<-56+2+2
larger_head_circu
```
### To do 3
```{r}
larger_head_circu2<-56+2
larger_head_circu2
```



## Overview the data
```{r}
stu_data<-read.csv("Student.csv")
head(stu_data)
class(stu_data)
```
## Observe the data
```{r}
counts <- table(stu_data$ReligImp)
counts
```
## pie chart
```{r}
lbls<-rownames(counts)
pie(counts, labels = lbls,  main="ReligImp") 

```

## Histogram
```{r}
library(ggplot2)
library(magrittr)
stu_data%>%ggplot(aes(x=ReligImp))+geom_bar()
```
# Find the outliers
```{r}
library(dplyr)
MyOutlierDetect<-function(vari,x){
  col<-read.csv("Student.csv")
  col<-select(stu_data,vari)
  col<-as.numeric(unlist(col))
  min<-quantile(col,na.rm = TRUE)[2]-1.5*IQR(col, na.rm = T)
  max<-quantile(col,na.rm = TRUE)[4]+1.5*IQR(col, na.rm = T)
  if (x<min|x>max){
    return("YES")
    }else{
    return("NO")  
  }
  return(s)

}
MyOutlierDetect("PartyDays",10)

```



